### 2014-01-23 Draft/approach.tex
publishing local file changes
Changed approach, Introduction

As described in Section~\ref{sub:SENLPback} the intermediate representation generation technique is based on the principle of shallow parsing~\cite{Branimir2000}. 
In particular, the intermediate-representation technique is implemented as a function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,SNLP,KleinNIPS03}, to leverage the semantic information encoded in Stanford-typed dependencies.

@@

This component accepts the FOL representation of the sentence.

\begin{itemize}
\item Extracts Specifications from FOL representation. 
\item Specifically looking for modal modifies ``can, could, may, must, should'' 
\item Takes into consideration the negative quantifiers.
\item Algorithm to infer the sequence of operations.
\end{itemize}

\subsection{Postprocessor}
\label{sub:postpro}
undoing pre-processing and Hybrid intermediate representation generation.

@@

@@

A key way of identifying reference to a method within the API in our proposed approach is the employment of a semantic graph of an API.
In particular, we propose to initially infer such graphs from API documents.
Manually creating a semantic graph is prohibitively time consuming and may be error prone.
We thus employ a systematic methodology (proposed previously in ~\cite{pandita13:WHYPER}) to infer such semantic graphs from API documents that can potentially be automated.
We first consider the name of the class.
We then find the synonyms terms used refer to the class in question.
The synonym terms are listed as by breaking down the camel-case notation in the class name.
This list is further augmented by listing the name of the parent classes and implemented interfaces if any.

@@

@@

\FORALL{$Method\ mtd\ in\ methodList$} 
	\IF{$mtd.isPublic()$}
		\IF{$!mtd.isStatic()$}
			\STATE $List\ preList\ =\ idx.query(mtd.declaringType)$
			\FORALL{$Method\ mtd'\ in\ preList$}
				\STATE $seq\_Graph.addEdge(mtd',mtd)$
			\ENDFOR
		\ENDIF
		\FORALL{$Parameter\ param\ in\ mtd.getParameters()$}
			\IF{$!isBasicType(param.Type)$}
				\STATE $List\ preList\ =\ idx.query(paramType)$
				\FORALL{$Method\ mtd'\ in\ preList$}
					\STATE $seq\_Graph.addEdge(mtd',mtd)$
				\ENDFOR				
			\ENDIF
		\ENDFOR
	\ENDIF
\ENDFOR
\RETURN $seq\_Graph$
\end{scriptsize}
\end{algorithmic}
\caption{Type\_Sequence\_Builder}
\label{alg:SeqAnnotaator}
\end{algorithm}

%The FOL representation helps us effectively deal with the problem of \emph{confounding effects} of keywords as described in Section~\ref{sec:overview}. In particular, the FOL assists in distinguishing between a resource that would be a leaf node and an action that would be a predicate node in the intermediate representation of a sentence. The generated FOL representation of the sentence is then provided as an input to the semantic engine for further processing.
%
%
%
%\subsection{Semantic Engine (SE)}
%\label{sub:SE}
%The Semantic Engine (SE) accepts the FOL representation of a sentence and based on the semantic graphs of Android permissions annotates a sentence if it matches the criteria. A semantic graph is basically a semantic representation of the resources which are governed by a permission. For instance, the READ\_CONTACTS permission governs the resource ``CONTACTS'' in Android system.
%
%
%Figure~\ref{fig:knowledge} shows the semantic graph for the permission READ\_CONTACTS. A semantic graph primarily constitutes of subordinate resources of a permission (represented in rectangular boxes) and a set of available actions on the resource itself (represented in curved boxes). Section~\ref{sub:ACA} elaborates on how we build such graphs systematically.
%
%Our SE accepts the semantic graph pertaining to a permission and annotates a sentence based on the algorithm shown in Algorithm~\ref{alg:SenAnnotaator}. The Algorithm accepts the FOL representation of a sentence $rep$, the semantic graph associated with the resource of a permission $g$ and a boolean value $recursion$ that governs the recursion. The algorithm outputs a boolean value $isPStmt$, which is \CodeIn{true} if the statement describes the permission associated with a semantic graph ($g$), otherwise \CodeIn{false}. 
%
%Our algorithm systematically explores the FOL representation of the sentence to determine if a sentence describes the need for a permission. First, our algorithm attempts to locate the occurrence of associated resource name within the leaf node of the FOL representation of the sentence (Line 3). The method \CodeIn{findLeafContaining(name)} explores the FOL representation to find a leaf node that contains term \CodeIn{name}. Furthermore, we use WordNet and Lemmatisation~\cite{Do09:Robust} to deal with synonyms of a word in question to find appropriate matches. Once a leaf node is found, we systematically traverse the tree from the leaf node to the root, matching all parent predicates as well as immediate child predicates [Lines 5-16].
%
%Our algorithm matches each of the traversed predicate with the actions associated with the resource defined in semantic graph. Similar to matching entities, we also employ WordNet and Lemmatisation~\cite{Do09:Robust} to deal with synonyms to find appropriate matches. If a match is found, then the value \CodeIn{isPStmt} is set to  \CodeIn{true}, indicating that the statement describes a permission.
%
%In case no match is found, our algorithms recursively search all the associated subordinate resources in the semantic graph of current resource. A subordinate resource may further have its own subordinate resources. Currently, our algorithm considers only immediate subordinate resources of a resource to limit the false positives.
%
%%We limit the exploration to depth 1 to limit the false positives. That means only immediate subordinate resources of a resource will be explored.
%
%In the context of the FOL representation shown in Figure~\ref{fig:FOLRep}, we invoke Algorithm~\ref{alg:SenAnnotaator} with the semantic graph shown in Figure~\ref{fig:knowledge}. Our algorithm attempts to find a leaf node containing term ``CONTACT'' or some of its synonym. Since the FOL representation does not contain such a leaf node, algorithm calls itself with semantic graphs of subordinate resources (Line 17-25), namely `NUMBER', `EMAIL', `LOCATION', `BIRTHDAY', `ANNIVERSARY'. 
%
%The subsequent invocation will find the leaf-node ``email'' (annotated 9 in Figure~\ref{fig:FOLRep}). Our algorithm then explores the preceding predicates and finds predicate ``share'' (annotated 2 in Figure~\ref{fig:FOLRep}). The Algorithm matches the word ``share'' with action ``send'' (using Lemmatisation and WordNet similarity), one of the actions available in the semantic graph of resource `EMAIL' and returns \CodeIn{true}. Thus, the sentence is appropriately identified as describing the need for permission READ\_CONTACT. 
%
%

>>>>

As described in Section~\ref{sub:SENLPback} the intermediate representation generation technique is based on the principle of shallow parsing~\cite{Branimir2000}. 
In particular, the intermediate-representation technique is implemented as a function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,KleinNIPS03}, to leverage the semantic information encoded in Stanford-typed dependencies.

@@

@@

This component accepts the FOL representation of the sentence from the previous component,
then extracts the temporal constraints if present in a sentence. 
Specification Extractor then classifies the sentence as a specification 
sentence (containing temporal constraint) candidate based on following ordered set of rules:

\begin{enumerate}
	\item The sentence is not from parameter summary or return variable summary.
	Typically such sentences describe pre-post conditions as opposed to temporal constraints this approach addresses.
	\item The sentences contains modal modifiers such as ``can, could, may, must, should'' expressing necessity.
	Typically, presence of such modal modifier is a strong indicator of presence of constraints imposed by an API developer
	\item If the sentence does not contain modal modifiers described previously, sentence must contain temporal modifier relationship, identified by Stanford-typed dependency parser.
	Typically, presence of temporal modifier is an indicator of presence of temporal information.  
	\item If rules 2 and 3 don't apply then the sentences should be a conditional sentence, identified by the presence of keywords such as ``if''.
\end{enumerate}

Once a candidate sentence is identified, this component selects an semantic graph.
In particular, the semantic graph of the API class to which the candidate sentence belongs to selected.
A semantic graph constitutes the keyword representation of the classes and the corresponding applicable actions. 
Figure~\ref{fig:knowledge} shows a sub-graph of  graph for \CodeIn{BufferedInputReader} class.
The phrases in solid rectangles are synonyms of the class name \CodeIn{BufferedInputReader}.
The phrases in rounded rectangle are the actions applicable on \CodeIn{BufferedInputReader} class.
Section~\ref{sub:ACA} further describes how these graphs are generated.

Specification extractor then uses the semantic graph to determine
if a candidate sentence is a specification sentence and if so extract
the action that is should be performed prior to the method the sentence
belongs to. Algorithm~\ref{alg:SenAnnotaator} describes this action extraction
process.

Our algorithm systematically explores the FOL representation
of the candidate sentence to determine if a sentence
describes a temporal specification. First, our algorithm
attempts to locate the occurrence of class name or its synonym
within the leaf nodes of the FOL
representation of the sentence (Line 3). The method
findLeafContaining(r\_name\_list) explores the FOL representation
to find a leaf node that contains either the class name
or one of its synonyms.
In particular, we use WordNet~\cite{wordnet} and Lemmatisation
to deal with synonyms of a word in question to find appropriate
matches. Once a leaf node is found, we systematically
traverse the tree from the leaf node to the root,
matching all parent predicates as well as immediate child
predicates [Lines 5-16].

Our algorithm matches each of the traversed predicate
with the actions associated with the class defined in
semantic graph. Similar to matching entities, we also
employ WordNet and Lemmatisation to deal with
synonyms to find appropriate matches. If a match is
found, then the matching action name is returned.

@@

A key way of identifying reference to a method within the API in our proposed approach is the employment of a semantic graph of an API.
In particular, we propose to initially infer such graphs from API documents.
Manually creating a semantic graph is prohibitively time consuming and may be error prone.
We thus employ a systematic methodology (proposed previously in ~\cite{pandita13:WHYPER}) to infer such semantic graphs from API documents that can potentially be automated.
We first consider the name of the class for the API document in question.
We then find the synonyms terms used refer to the class in question.
The synonym terms are listed as by breaking down the camel-case notation in the class name.
This list is further augmented by listing the name of the parent classes and implemented interfaces if any.

@@

\subsection{Type Analysis}

As mentioned earlier that some temporal constraints are enforced by the type system in typed Languages.
For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$). To extend the temporal constraints inferred by the analyzing the natural language text, this component infers additional constraints that are encoded
in the type system. Algorithm~\ref{alg:TypeAnalysis} lists the steps followed to infer type based temporal constraints.

The algorithm accepts the list of methods as an input produces a graph with
the nodes representing methods in an API and the directed edges representing temporal constraints.
First, a index is created based on the return types of the method (Line 2).
Second, all methods in an API are added to an unconnected graph (Line 3-4).
Then, for every public method in the input list, the algorithm checks the types
of the input parameters and constructs and directed edge from all the methods that whose return value
have the same type to the method in question (Line 14- 20).
The algorithm does not take into consideration the basic parameter types such as integer, string (Line 15)
Additionally, an edge is created from the constructors of a class to the non static members methods of a class (Line 8 -13).
The resultant graph is then returned by the algorithm.

The temporal constraints based on the type information can be extracted by querying the graph. 
The incoming edges to a node denoting a method represents the set of pre-requisite methods.
The temporal constraint being, at least one of the pre-requisite methods must be invoked before invoking the method in question.

@@

\FORALL{$Method\ mtd\ in\ methodList$} 
	\IF{$mtd.isPublic()$}
		\IF{$!mtd.isStatic()$}
			\STATE $List\ preList\ =\ idx.query(mtd.declaringType)$
			\FORALL{$Method\ mtd'\ in\ preList$}
				\STATE $seq\_Graph.addEdge(mtd',mtd)$
			\ENDFOR
		\ENDIF
		\FORALL{$Parameter\ param\ in\ mtd.getParameters()$}
			\IF{$!isBasicType(param.Type)$}
				\STATE $List\ preList\ =\ idx.query(paramType)$
				\FORALL{$Method\ mtd'\ in\ preList$}
					\STATE $seq\_Graph.addEdge(mtd',mtd)$
				\ENDFOR				
			\ENDIF
		\ENDFOR
	\ENDIF
\ENDFOR
\RETURN $seq\_Graph$
\end{scriptsize}
\end{algorithmic}
\caption{Type\_Sequence\_Builder}
\label{alg:TypeAnalysis}
\end{algorithm}

### 2014-01-23 Draft/evaluation.tex
Changed approach, Introduction

We conducted an evaluation to assess the effectiveness of our approach. In our evaluation, we address two main research questions:

\begin{itemize}
	\item\textbf{RQ1}: What are the precision and recall of \tool\  in
	identifying temporal contraints from sentences written in natural language?
	%\item\textbf{RQ2}: What is the accuracy of our approach in inferring specifications from contract sentences in the API documents? 
	\item\textbf{RQ2}: How does our approach fares in comparison to previous NLP approaches?
\end{itemize}

@@

\subsection{Experimental Setup.} 
We apply our approach on the API documents of the two APIs.
To determine the precision and recall, 
two authors manually label each sentence in the API documentation as sentence containing 
temporal constraints or not. After the authors have classified all the sentences, they 
talk to each ther to reach a consensus on the sentences they classified differently. 
We use this classified scentes as the golden set for calculating precision and recall.

\CodeIn{cohen kappa} score of the two authors was 6.6

>>>>

We conducted an evaluation to assess the effectiveness of \tool. In our evaluation, we address two main research questions:

\begin{itemize}
	\item\textbf{RQ1}: What are the precision and recall of \tool\  in
	identifying temporal constraints from sentences written in natural language?
	\item\textbf{RQ2}: What is the accuracy of \tool\ in inferring temporal constraints from specification sentences in the API documents? 
\end{itemize}

@@

\subsection{Experimental Setup.} 
We first manually annotated the sentences in the API documents of the two APIs.
Two authors manually labeled each sentence in the API documentation as sentence containing 
temporal constraints or not.
We used \CodeIn{cohen kappa}~\cite{carletta1996assessing} score to statistically measure
the inter-rater agreement.
The \CodeIn{cohen kappa} score of the two authors was .66 (on a scale of 0 to 1), 
which denotes a statically significant agreement. 
After the authors classified all the sentences, they 
discussed with each other to reach a consensus on the sentences they classified differently. 
We use this classified sentences as the golden set for calculating precision and recall.

To answer RQ1, we measure the number of true positives ($TP$), false positives ($FP$), true negative ($TN$), and false negatives ($FN$)
in identifying the specification sentences by \tool.
We define specification sentence as a sentence describing a temporal constraints.
We define the $TP$, $FP$, $TN$, and $FN$ of \tool\ as follows:

\begin{enumerate}
	\item $TP$: A sentence correctly identified by \tool\ as specification sentence.
	\item $FP$: A sentence incorrectly identified by \tool as specification sentence.
	\item $TN$: A sentence correctly identified by \tool\ as not a specification sentence.
	\item $FN$: A sentence incorrectly identified by \tool\ as not a specification sentence.
\end{enumerate}

In statistical classification~\cite{Olson08}, $Precision$ is defined as a ratio of
number of true positives to the total number of items reported to be true,
$Recall$ is defined as a ratio of number of true positives to the total number
of items that are true. $F-score$ is defined as the weighted harmonic mean of 
$Precision$ and $Recall$. Higher value of $Precision$, $Recall$, and $F-Score$
are indicative of higher quality of the specification statements inferred using 
\tool. based on the calculation of $TP$, $FP$, $TN$, and $FN$ of \tool\ defined
previously we computed the $Precision$, $Recall$, and $F-Score$ of \tool\ as follows:

\begin{center}

$Precision$ = $\frac{TP}{TP + FP}$

$Recall$ = $\frac{FN}{TP + FP}$

$F-Score$ = $\frac{2 X Precison X Recall}{Precision + Recall}$

\end{center}

To answer RQ2, we checked the temporal constraints inferred from specification sentences by \tool.
We measure $accuracy$ of \tool as the ratio of the total number of temporal constraints that
are correctly inferred by \tool to the total number of specification sentences.

\subsection{Results}

We next describe our evaluation results to demonstrate the effectiveness of \tool\ in identifying temporal constraints.

\subsubsection{RQ1: Effectiveness in Identifying Specification Sentences}

In this section, we evaluate the effectiveness of \tool\ in identifying specification sentences from API documents.

We next describe how

\subsubsection{RQ2: Accuracy in Inferring Temporal Constraints}

In this section, we evaluate the effectiveness of \tool\ in inferring specification sentences from API documents.
